

\noindent 
During our Spring 2025 faculty retreat, I was assigned the task of drafting a \emph{B}ring \emph{Y}our \emph{O}wn \emph{D}evice (BYOD) policy for CS students. This draft policy outlines the system requirements. The earliest we can implement the policy is beginning in the academic year 2027-28, i.e, with the class of 2032.

The proposed policy is based on similar BYOD policy that I drafted in 2001 for the University of Chicago's Master of Computer Science program, as well as on current BYOD policies from \href{https://clemsonpub.cfmnetwork.com/B.aspx?BookId=11654&PageId=458060}{Clemson University}, \href{https://www.fit.edu/policies/information-technology/policies/it-1015-bring-your-own-device-byod-policy/}{Florida Institute of Technology}, and Northern Illinois University.
    


\section*{Timeline}


\begin{description}

    \item[April 2025] Consensus for BYOD policy at curriculum retreat. 
    \item[May 2025] Draft policy posted, RFC.
    \item[November 2025] Policy review at faculty meeting; changelog:
    \begin{itemize}
    \item Inclusion of Chromebooks;
    \item Expansion of policy to all CS majors and minors, graduate and undergraduate;
    \item Language for casual enrollees in COMP 170 etc. In addition to the language added here, LOCUS/catalog descriptions , at least, the following courses should mention the BYOD explicitly: COMP 125; COMP 141; COMP 150; COMP 170; COMP 264; COMP 271; COMP 272; COMP 363.
    \item Removal of specific OS versions, replaced with general language about current versions of major OSs;
    \item Addition of software requirements with clarification that MSOffice can run natively or in-browser;
    \item Modification of device age requirement from 6 years to 4 years, to align with requirement that system must be serviceable for the duration of studies (system will be at most 8 years old by senior year).
    \end{itemize}
    \item[December 2025] During curriculum retreat:
    \begin{itemize}
        \item Remove Chromobooks from the list of recommended devices, as they do not meet the software requirements for some cybersecurity courses.
        \item Soften language about insurance coverage from requirement to recommendation.
        \item Remove specific system recommendations, as they will be outdated by the time the policy is implemented. Instead, add language about recommended system specifications.
    \end{itemize}
    \item[April 2026] Draft answers to questions posed by CAS Dean.
    
    \end{description}

\section*{Next Steps}

\begin{itemize}
    \item Share with ITS for feedback.
    \item Share with administration for approval.
\end{itemize}


\newpage