

\newpage\section*{Dean's Cabinet Q\&A}

\noindent 
In March 2026, the department received feedback from the CAS Dean Cabinet. This section addresses some/as many of the questions posed by the cabinet.

% I am so ashamed of my vskips below, but I don't have tme to templetize a nice Q&A format.

\subsubsection*{What is approximately the cost of needed software or licenses (if needed) and would any discounts be available, for example if 100 student utilize it can either software or hardware be discounted?}

The software our students need is either directly free, free with an academic license, or free because it's covered by Loyola already (eg, Office 365 and TechConnect). 

\subsection*{Have you considered that charging towers might be a necessity for the students?} 

Yes, and that is one reason we recommend relatively recent laptops with battery life sufficient for a full day of classes, thereby minimizing or eliminating the need for charging stations. The installation of charging infrastructure, however, is beyond the department’s capacity. Equipping classrooms for contemporary instruction is ultimately an institutional responsibility and charging towers are the \emph{least} of the challenges we face in the classroom for CS instruction. Ample desk surface is far more critical and absent from most classrooms in Mundelein Center or Dumbach Hall. Faculty have previously offered recommendations regarding classroom requirements for adequate Computer Science instruction, though those suggestions have not been acted upon.

\subsubsection*{Have you explored a grant covering this?} 

Yes, but at present that does not appear to be a viable path. In the past, vendors such as Dell sometimes offered substantial discounts to students through university partnerships, packaged as grants and tied to broader service or equipment contracts. That model seems far less common now, likely because margins are tighter and many institutions have shifted significant portions of IT support and infrastructure to SaaS-based providers. We are not aware of foundations or agencies that routinely fund student equipment needs, except for underserved populations and communities. We will explore potential grant opportunities brought to our attention, but we should not delay implementation of this policy in the hope that such funding may materialize.

\subsubsection*{Check with our school of business and with the school of nursing to see how they manage their programs that strongly recommend computers. Note in your proposal how this is handled.} 

While it may be useful to know what other units do, our decision should ultimately rest on the nature of computer science itself. Computing is not peripheral to our discipline; it is the discipline. For that reason, our expectations around student access to computing platforms are likely to be more central, and more academically justified, than in many other programs.

\subsubsection*{How will you handle this for students who show an economic need and cannot afford the laptop?} 

These cases should be addressed individually and with flexibility. Some students may be able to obtain suitable refurbished equipment at substantially lower cost through vendors such as Newegg or similar sources. In addition, we could explore establishing a modest departmental or institutional fund to support a small loaner pool of laptops for students with demonstrated financial need. 


\subsubsection*{AJCU practices} 

The following is a list of AJCU institutions with BYOD policies for their Computer Science students. This list suggest that such policies are not uncommon among our peer institutions. Another 14 institutions have strongly recommended BYOD policies, but do no require students to have their own devices. A simple scan of various faculty course descriptions and syllabi from these institutions conducted by a Claude agent, found that several instructors have course-specific requirements for students to have their own devices, even in the absence of a formal BYOD policy, across the majority of AJCU computer science programs.

\begin{itemize}

    \item University of San Francisco — The Computer Science department requires students to have a laptop that meets minimum specifications. University of San Francisco

    \item Gonzaga University — The School of Engineering and Applied Science explicitly states students "are required to have your own laptop." Gonzaga University Computer Science students may bring an Apple MacBook Pro, while engineering students are limited to Windows PCs. 

    \item Seattle University — Starting in Fall 2025, the Computer Science department requires students to have laptops for use in computer science courses. Seattle University

    \item Creighton University — All Creighton University students (not just CS) are required to have a laptop computer that meets or exceeds minimum requirements. Creighton University This is a university-wide mandate.
    
    \item Marquette University — All engineering students are required to have a laptop computer that meets minimum specifications.
    
    \item Rockhurst University — All undergraduates in the College of Business and Technology are required to have access to a laptop to bring to classes. 

\end{itemize}