\section{Qualified Devices}

A \emph{qualified device} is a system that meets the expectations of this policy, by featuring the following characteristics.

\subsection*{Minimum Requirements}
    
\begin{description}

    \item [Screen.] The device's screen must have at least a 10-inch diagonal, a 16:9 aspect ratio (or comparable aspect ratio), and at least $1204\times 768$ pixels resolution.

    \item [Keyboard.] The device must have a separate physical keyboard. 

    \item[Memory.] At least 16 GB of memory.

    \item[Storage.] At least 128 GB of storage.

    \item[Neworking.] WiFi capable, compatible with IEEE 802.11ac (also known as WiFi-5) or higher.

    \item[Battery life.] A fully charged system should be able to run for at least 6-7 hours.

    \item[Tracking.] The device must be trackable so that it can be located if forgotten/stolen.

    \item[No older than 6 years.]

    \item[Portable.] The system must be light enough to be carried around campus comfortably and not require excessive space on a classroom desk.

    \item[Operating system.] A qualified device must be capable of running one of the following operating systems or higher: Windows 11, MacOS Sonoma, Ubuntu 20.04, or Kali 2025.1a.\linelabel{line:os}

    \item[Software.] The system must be capable of running the current version of the following applications: any major browser (Google Chrome, Microsoft Edge, or Apple Safari), Microsoft Teams, Microsoft Office (at least Outlook, Word and Powerpoint), and Adobe Acrobat. Furthermore, the system must be capable of supporting these applications and their future updates for the duration of your studies at LUC.

    \item[Access to Command Line Interface.] The system must have a feature that allows direct access to the command line interface. For example, the Terminal application in MacOS, Windows, and Linux machines. 
    
\end{description}

\subsection*{Optional Requirements}

\begin{description}
    \item[Expandable.] The system should be able to connect to various peripherals such as a larger screens (if you have one in your residence), printers, etc. 
    
    \item[Protection.] The device must be covered by a protection policy (an insurance policy to cover serious repairs and provide replacement in case of major damage).

\end{description}